\addwork%
{%
    2020--Present;% don't forget the semicolon!!!
    Scientific Collaborator;% don't forget the semicolon!!!
    Fraunhofer Institute Italia;% don't forget the semicolon!!!
    \begin{itemize}
        \item Robotic system integration with ROS
        \item Motion control for collaborative robotics
        \item CI/CD for robotic applications
    \end{itemize}
}%
\addwork%
{%
    2017--2020;% don't forget the semicolon!!!
    Research Assistant;% don't forget the semicolon!!!
    Free University of Bozen-Bolzano;% don't forget the semicolon!!!
    \begin{itemize}
        \item Work package leader of European and Internal projects.
        \item Project writing
        \item IoT responsible of the Smart-minifactory laboratory.
            \ifdefined\extended
                \begin{enumerate}
                    \item Implementation of protocols XMPP, MQTT, XMLRPC, REST, ROS for communication and NFS and SAMBA for storage.
                    \item NAT implementation for legacy local networks using Mikrotik routers and Raspberry.
                    \item Programming embedded IoT-oriented application for robotic platforms \href{https://github.com/rafaelrojasmiliani/vplusxmlrpc}{https://github.com/rafaelrojasmiliani/vplusxmlrpc}
                \end{enumerate}
            \fi
        \item Lecturer of Flexsim for Simulation in Production and Logistics             
    \end{itemize}
}%
\addwork%
{%
    2020--2021;% don't forget the semicolon!!!
    Tecnologo;% don't forget the semicolon!!!
    Free University of Bozen-Bolzano;% don't forget the semicolon!!!
    \begin{itemize}
        \item Implementation AI Planning on Robotic Application
        \item Research on Optimization for Motion planning in Robotics
            \ifdefined\extended
                \begin{enumerate}
                    \item Theoretical development of optimization framework based on the Calculus of Variations.
                    \item Implementation of optimization algorithm using Python as well as interfaces for IPOPT and MOSEK.
                    \item \href{https://gitlab.inf.unibz.it/smartminifactory/apps}{https://gitlab.inf.unibz.it/smartminifactory/apps} Minimum jerk motions for Universal Robots.
                    \item Currently development and implementing of a novel prescribed path minimum-time optimization.
                \end{enumerate}
            \fi
    \end{itemize}
}%
%\addwork%
%{%
%    2018--Present;% don't forget the semicolon!!!
%    Team member;% don't forget the semicolon!!!
%    Research project \emph{E-EDU 4.0--Engineering Education 4.0};% don't forget the semicolon!!!
%}%
%\addwork%
%{%
%    2017--Present;% don't forget the semicolon!!!
%    Work sub-package leader: ICT Technologies for Smart Manufacturing;% don't forget the semicolon!!!
%    Research project \emph{SME 4.0};% don't forget the semicolon!!!
%}%
%
%\addwork%
%{%
%    2018--2019;% don't forget the semicolon!!!
%    Consultant;% don't forget the semicolon!!!
%    Modal;% don't forget the semicolon!!!
%    \begin{itemize}
%        \item Implementation of IoT solutions for Raspberry and Alexa applications (bash scripting and NATting).
%        \item Implementation of XMLRPC and XMPP services and messages in Python and PROSODY.
%    \end{itemize}
%}%
%\addwork%
%{%
%    2019--Present;% don't forget the semicolon!!!
%    Consultant;% don't forget the semicolon!!!
%    Matt\& Partner;% don't forget the semicolon!!!
%    Development and implementation of Virtual Twin of the Emergency Room of the Hospital of Bolzano.%
%    \begin{itemize}
%        \item Team coordination for data acquisition, identification of key performance indicators and emergency room processes dynamics
%        \item Programming of the simulation model in Flexsim and data acquisition
%        \item Scientific support for the improvement of the actual emergency room
%    \end{itemize}
%}%
