\addskill%
{%
    \underline{Languages}:%
    \begin{multicols}{2}
        \begin{itemize}[nosep, rightmargin=0cm,after*={\vspace{-\baselineskip}}]%
            \item {\em Spanish}: mother tongue.
            \item {\em Italian}: fluent (C2).
            \columnbreak
            \item {\em English}: good (C1).
            \item {\em German}: Beginner (A2).
        \end{itemize}%
    \end{multicols}
}%

%\addskill%
%{%
%    \underline{Some knowledge field}:%
%    \begin{itemize}[nosep, rightmargin=0cm]%
%        \item Some topic.
%        \item Another topic.
%        \item Some other topic.
%    \end{itemize}%
%}%
%
%\addskill%
%{%
%    \underline{Another knowledge field}:%
%    \begin{itemize}[nosep, rightmargin=0cm]%
%        \item Some topic.
%        \item Another topic.
%        \item Some other topic.
%    \end{itemize}%
%}%

\addskill%
{%
    \underline{Software Development}:%
    \begin{itemize}[nosep, rightmargin=0cm]%
        \item Languages: C, C++ and Python.%
        \item Scientific: MATLAB/Simulink, gnuplot, Eigen, GSL, CASADI.%
        \item Optimizers: IPOPT, MOSEK, SNOPT.%
        \item CVS and CI/CD: git, Jenkins, Github Actions, Aptly.%
        \item Build systems: catkin, colcon GNU Make, CMake, GDB.%
        \item Microsoft Office Suite and TeX/LaTeX.%
    \end{itemize}%
}%
\addskill%
{%
    \underline{Contribution to open source projecs}:%
    \begin{itemize}[nosep, rightmargin=0cm]%
        \item MoveIt (\url{https://github.com/ros-planning/moveit/}): Pull request \href{https://github.com/ros-planning/moveit/pull/2563}{2563}, code quality and pull request \href{https://github.com/ros-planning/moveit/pull/2663}{2668} urdf to collision object conversion .
        \item Python Robotics (\url{https://github.com/AtsushiSakai/PythonRobotics/}): Pull request  \href{https://github.com/AtsushiSakai/PythonRobotics/pull/401}{401}, code quality and motion planning algorithm improvement.
        \item Franka ROS (\url{https://github.com/frankaemika/franka_ros}): Pull request \href{https://github.com/frankaemika/franka_ros/pull/176}{176}, bug fixing.
    \end{itemize}%
}%
\addskill%
{%
    \underline{Embedded systems experience and programming}:%
    \begin{itemize}[nosep, rightmargin=0cm]%
        \item Robotic OS: Adept V+, Linux.%
        \item Robotic Platforms: Adept QUATTRO and COBRA, Universal Robots UR3 and UR10 (CB3), Kuka iiwa and KMP%
    \end{itemize}%
}%

%\addskill%
%{%
%    \underline{Other interests}: hobbies and so on.
%}%
